Mentored data science research with tweets

### 2020-04-18 Rmd/jse-2019-ms.Rmd
added text to ms

>>>>

As a proof of principle of our event detection strategy, we chose to 
examine tweets before, during, and after the National Football League's 
2015 Super Bowl. We fitted five latent Dirichlet allocation models. We examined five time periods, each lasting one hour in duration. The first period began approximately 48h before the Super Bowl halftime show. Subsequent time periods started at -24, 0, +24, and +48 hours after the approximate start time of the halftime show.

We defined each time period to be a single corpus of tweets. We then fitted latent Dirichlet allocation models to each corpus.
